---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Homework6

<!-- badges: start -->
[![R-CMD-check](https://github.com/akash-rajeev/Homework6/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/akash-rajeev/Homework6/actions/workflows/R-CMD-check.yaml)
[![R-CMD-check](https://github.com/akash-rajeev/Homework6/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/akash-rajeev/Homework6/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of Homework6 is to create a package that allows for basic operations on sparse matrices. Contains several methods relating to the development of sparse matrices, including arithmetic operations, statistical operations, and display operations.

## Installation

You can install the development version of Homework6 in github like so:

``` r
# install.packages("devtools")
devtools::install_github("akash-rajeev/Homework6)
```


## Example

Here are some basic examples relating to the package
```{r example, message=FALSE, warning=FALSE}
library(Homework6)

# Create a regular numeric vector
regular_vec = c(0, 1.5, 0, 0, 2.3, 0, 0, 4.1, 0, 0)

# Convert to sparse format
sparse_vec = as(regular_vec, "sparse_numeric")
print(sparse_vec)

# Create another sparse vector
regular_vec2 = c(0, 0.5, 0, 1.0, 2.3, 0, 0, 0, 3.2, 0)
sparse_vec2 = as(regular_vec2, "sparse_numeric")

# Arithmetic operations
sum_vec = sparse_vec + sparse_vec2
print(sum_vec)
diff_vec = sparse_vec - sparse_vec2
print(diff_vec)

```


